### 2016-07-22 inst/vign/name_cleaning.Rmd
#549 name cleaning vignette work

## xxx

```{r}
"asdfasfsf"
```

>>>>

## get_* functions

When using `get_*()` functions programatically, you have a few options.

### rows parameter

Normally, if you get more than one result, you get a prompt asking you
to select which taxon you want.

```{r eval=FALSE}
get_tsn(searchterm = "Quercus b")
#>       tsn                       target             commonnames    nameusage
#> 1   19298             Quercus beebiana                         not accepted
#> 2  507263       Quercus berberidifolia               scrub oak     accepted
#> 3   19300              Quercus bicolor         swamp white oak     accepted
#> 4   19303             Quercus borealis                         not accepted
#> 5  195131 Quercus borealis var. maxima                         not accepted
#> 6  195166            Quercus boyntonii Boynton's sand post oak     accepted
#> 7  506533              Quercus brantii             Brant's oak     accepted
#> 8  195150            Quercus breviloba                         not accepted
#> 9  195099              Quercus breweri                         not accepted
#> 10 195168             Quercus buckleyi               Texas oak     accepted
#>
#> More than one TSN found for taxon 'Quercus b'!
#>
#>             Enter rownumber of taxon (other inputs will return 'NA'):
#>
#> 1:
```

Instead, we can use the rows parameter to specify which records we want
by number only (not by a name itself). Here, we want the first 3 records:

```{r eval=FALSE}
get_tsn(searchterm = 'Quercus b', rows = 1:3)
#>     tsn           target     commonnames    nameusage
#> 1 19298 Quercus beebiana                 not accepted
#> 2 19300  Quercus bicolor swamp white oak     accepted
#> 3 19303 Quercus borealis                 not accepted
#>
#> More than one TSN found for taxon 'Quercus b'!
#>
#>             Enter rownumber of taxon (other inputs will return 'NA'):
#>
#> 1:
```

However, you still get a prompt as there is more than one result.

Thus, for full programmatic usage, you can specify a single row, if you happen
to know which one you want:

```{r}
get_tsn(searchterm = 'Quercus b', rows = 3)
```

In reality it is unlikely you'll know which row you want, unless perhaps you 
just one one result from each query, regardless of what it is.

### underscore methods

A better fit for programmatic use are underscore methods. Each `get_*()` function
has a sister method with and trailing underscore, e.g., `get_tsn()` and `get_tsn_()`.

```{r}
get_tsn_(searchterm = "Quercus b")
```

The result is a single data.frame for each taxon queried, which can be 
processed downstream with whatever logic is required in your workflow.

You can also combine `rows` parameter with underscore functions, as a single
number of a range of numbers:

```{r}
get_tsn_(searchterm = "Quercus b", rows = 1)
```

```{r}
get_tsn_(searchterm = "Quercus b", rows = 1:2)
```

## gnr_resolve

Some functions in `taxize` are meant specifically for name cleaning. One of those
is `gnr_resolve()`.

`gnr_resolve()` doesn't provide prompts as do `get_*()` functions, but instead
return data.frame's. So we don't face the same problem, and can use `gnr_resolve()` 
in a programmatic workflow straight away.

```{r}
spp <- names_list(rank = "species", size = 10)
gnr_resolve(names = spp, preferred_data_sources = 11)
```
